\documentclass{class}
\usepackage{multicol}
\usepackage{float}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{array}
\usepackage{caption}
\usepackage{enumitem} % Customize bullet lists
\usepackage{listings} % Code listings

%% Abbreviated author list for the running footer
\bibliography{References}

\abstract{This report explores the vast landscape of book reviews within the Amazon Books Review dataset through the lens of data science. Our mission was to uncover meaningful insights, sentiments, and correlations embedded in this extensive collection of reviews. Leveraging advanced tools and technologies such as Hadoop, Spark, MongoDB, and Python libraries, we embarked on a journey to understand the impact of various factors on review helpfulness.
Our approach involved meticulous data preparation, hypothesis generation, and hypothesis testing. We investigated the influence of review length, sentiment, and ratings on review helpfulness, shedding light on the intricate interplay between these variables. Additionally, we ventured into the realm of helpfulness prediction using Word2Vec and machine learning models, with Random Forest emerging as a standout performer.
Exploring user profiles and book categories, we gained valuable insights into user behavior and preferences, as well as the role of book categories in shaping review ratings. Throughout our journey, we encountered challenges that only fueled our determination to unearth hidden patterns in the data.
This report stands as a testament to the power of data science in deciphering the complexities of book reviews and provides a glimpse into the vast potential for innovation within the realm of big data. It underscores the importance of data-driven decision-making and sets the stage for further exploration and refinement of the insights gained, as we continue our mission to unravel the secrets hidden within data.}

\keywords{Big Data • Hadoop • Spark • ML • MongoDB • Data Analysis • Data Visualization • Python}
% Publication Title
\title{From Raw Data to Informed Decisions:\\ Analyzing Amazon Book Reviews}
% Short title for the header (copy the main title if it is not too long)
\shorttitle{Analysis of Amazon Book Reviews}

% Authors
\author[1]{Alberti A. Ligari D. Andreoli A.}
% Author Affiliations
\affil[1]{Data Science and Big data Analytics course, University of Pavia, Department of Computer Engineering (Data Science), Pavia, Italy}
% Surname of the first author of the manuscript
\firstauthor{Ligari Alberti Andreoli}
% Publication data (will be defined in the edition)
\publicationdate{\today}
% Place your particular definitions here
\newcommand{\vect}[1]{\mathbf{#1}}  % vectors
\github{https://github.com/DavideLigari01/data-science-project}

\begin{document}

\maketitle

\tableofcontents

\thispagestyle{FirstPage}

\input{./sections/introduction.tex}

\input{./sections/discovery.tex}

\input{./sections/data_preparation.tex}
\pagestyle{OtherPage}
\input{./sections/data_aggregation.tex}

\input{./sections/mongoDB_loading.tex}

\section{Local Hypotheses Testing}
\input{./sections/hypothesis_1.tex}
\subsection*{Hypothesis 2}
\input{./sections/hypothesis_3.tex}
\input{./sections/hypothesis_4.tex}
\input{./sections/hypothesis_5.tex}
\input{./sections/hypothesis_6.tex}
\input{./sections/spark_hypotheses_testing.tex}
\input{./sections/helpfulness.tex}
\input{./sections/conclusions.tex}


\input{./sections/codes.tex}

\end{document}
