\section{Data Preparation}
To commence our project, we initiated the process of data retrieval and preparation.

\subsection*{Data Retrieval and Preliminary Analysis}
The selected dataset comprises two tables and approximately three million reviews, accessible at the following link: \href{https://www.kaggle.com/datasets/mohamedbakhet/amazon-books-reviews}{Amazon Books Reviews}.
After acquiring the dataset, we executed the following steps:\\
\noindent

1. \textbf{HDFS Loading:} We loaded the data into HDFS using the following commands:

\begin{lstlisting}[language=bash, frame=single, basicstyle=\footnotesize\ttfamily, breaklines=true]
# Create HDFS directories
hdfs dfs -mkdir -p "$HDFS_PATH/ratings"
hdfs dfs -mkdir -p "$HDFS_PATH/books_info"

# Copy local files to HDFS
hdfs dfs -copyFromLocal "$LOCAL_PATH/ratings.csv" "$HDFS_PATH/ratings/"
hdfs dfs -copyFromLocal "$LOCAL_PATH/books_info.csv" "$HDFS_PATH/books_info/"
\end{lstlisting}

\noindent
2. \textbf{Preliminary Analysis:} We utilized PySpark to gain a comprehensive understanding of the data. During this phase, we defined a schema for our data and computed essential statistics, including the percentage of missing values and unique values for each field in our dataset.

\subsection*{Hypothesis Generation}
Following the preliminary analysis, we formulated several hypotheses for testing:

\begin{itemize}[leftmargin=*, noitemsep]
    \item \textbf{H1:} Reviews with longer text exhibit higher helpfulness ratings.
    \item \textbf{H2:} Reviews containing more positive sentiment words receive higher helpfulness ratings.
    \item \textbf{H3:} Reviews associated with higher book ratings correlate with higher helpfulness ratings.
    \item \textbf{H4:} Rating scores are influenced by individual users, potentially leading to overestimation or underestimation of a book's quality. Anonymous users may tend to underrate books.
    \item \textbf{H5:} The review score is influenced by the category of the book.
    \item \textbf{H6:} An increase in the number of books published within a category or by a particular publisher results in higher review scores.
\end{itemize}

\subsection*{Data Cleaning}
In this phase, we cleaned the data, addressing duplicates, eliminating extraneous columns for our analysis, and removing any symbols that could potentially interfere with the reading of the CSV files. All cleaning operations were executed using PySpark.
