\section{Discovery}
To initiate our data science initiative, it was important to assemble our team, precisely define our project's objectives, 
and conduct a comprehensive assessment of the available tools.

\subsection*{Team}
The team is composed by three members:

\noindent
\textit{Andrea Alberti}: \href{https://github.com/AndreaAlberti07}{github.com/AndreaAlberti07}\\
\textit{Davide Ligari}: \href{https://github.com/DavideLigari01}{github.com/DavideLigari01}\\
\textit{Cristian Andreoli}: \href{https://github.com/CristianAndreoli94}{github.com/CristianAndreoli94}\\

\subsection*{Framing}
The primary \textbf{objective} of this project is to craft a \textbf{scalable} solution for the comprehensive analysis of a dataset comprising 
Amazon book reviews. Ultimately, our aim is to construct a predictive model capable of assessing the helpfulness of a review based on its content.

\subsection*{Tools}
The selection of our tools was driven by the objective of crafting a scalable solution that can effectively operate within a \textbf{Big Data} environment.

\begin{itemize}[leftmargin=*, noitemsep]
    \item \textbf{Virtual Machine}: Employed to establish a controlled working environment.
    \item \textbf{Hadoop}: Utilized for the storage of data within a distributed file system and for executing MapReduce operations.
    \item \textbf{Spark}: Chosen as an enhanced alternative to MapReduce, facilitating operations on distributed datasets.
    \item \textbf{Python}: Adopted as the primary programming language due to its extensive library support.
    \item \textbf{MongoDB}: Implemented as a NoSQL database sandbox, ensuring secure handling of local data.
    \item \textbf{GitHub}: Employed for seamless project sharing and collaborative development.
    \item \textbf{LaTeX}: Utilized for the creation of the project report, ensuring professional and structured documentation.
\end{itemize}





