\section{Spark Hypotheses Testing}
To showcase the feasibility of implementing data analysis within a Big Data context, we opted to replicate some hypothesis testing using
Spark, focusing particularly on Hypotheses 1 and 3.

\subsection*{Hypothesis 1}
Addressing this hypothesis involved several key steps:

\begin{itemize}[leftmargin=*, noitemsep]
      \item \textbf{Compute the Helpfulness Score:}
            This was straightforwardly achieved by leveraging the `WithColumn` method of the Spark DataFrame, creating a new column with the updated values.

      \item \textbf{Compute the Text Length:}
            Text length computation was accomplished by utilizing `regexp\_replace` to eliminate punctuation, along with `Tokenizer` and `StopWordsRemover`
            to tokenize the text and remove stop words. Subsequently, a new column containing the text length was generated.

      \item \textbf{Bucketize the Text Length:}
            To address this requirement, we utilized the `Bucketizer` class from Spark MLlib in conjunction with a User Defined Function (UDF) to
            assign appropriate labels to the classes.

      \item \textbf{Compute the Correlation Coefficient:}
            Finally, the correlation coefficient was computed using the `Correlation.corr` method from Spark MLlib, specifically the Spearman correlation
            coefficient. The data was reshaped to conform to the required format using `VectorAssembler`.

\end{itemize}

\subsection*{Hypothesis 2}
To examine this hypothesis, we utilized Spark MLlib's capabilities to build a Naive Bayes model.
This model was trained to identify positive words within the dataset.
Following this, we computed the occurrence of the top 800 most positive words in each review.\\
We then obtained a Spearman correlation coefficient between helpfulness score and number of positive words of 0.318.
\subsection*{Hypothesis 3}
This hypothesis involved computing the helpfulness score and correlation coefficient, both of which were calculated using the same methods
described in the previous hypothesis.

\subsection*{Results}
In all test cases, the results closely mirrored those obtained in the local environment.

